HO unification from object language to meta language

### 2024-03-29 paper/main.tex
better display
mv printLink to printCompPb
some updates
update macro display pb

\newcommand{\lhs}{\ensuremath{\mathrm{lhs}}\xspace}
\newcommand{\rhs}{\ensuremath{\mathrm{rhs}}\xspace}

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. The compilation of each term would generate the
following result:

\begin{description}
  \item[Unif problems:] $X = \lambda x.\lambda y.x, Z = f\appsep(\lambda x.x)$
  \item[Mappings:] $\mapping{F}{G}{1}, \mapping{F}{H}{2}$  
  \item[Links:] $\linketaM{x}{Y_{x}}{\lambda y.H_{y~x}}$,\\
                $\linketaM{}{X}{\lambda x.Y_{x}}$,\\
                $\linketaM{}{Z}{\lambda x.f \appsep G_{x}~x}$
\end{description}

@@

The complete problem to run for resolution is now:

\newcommand{\printMinipage}[1]{
  \listlength{#1}
  \foreach \x [count=\i] in #1
    {
      \begin{minipage}{2.8cm}
        $\x$ %
      \end{minipage}
      \ifthenelse{\equal{\i}{\thellength}}{}{
        \ifthenelse{\isodd{\i}}{|}{\\}
      }
    }
}

\newcommand{\printLinks}[3]{
  \noindent
  \begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Unif problems:}]
    \item[Unif problems:] \printMinipage{#1}
    \item[Mappings:] \printMinipage{#2}
    \item[Links:] \printMinipage{#3}
  \end{description}
}

\printLinks{{
  X = \lambda x.\lambda y.x, 
  Z = f\appsep(\lambda x.x)}}
  {{\mapping{F}{H}{2}}}{{
  \linketaM{x}{Y_{x}}{\lambda y.H_{y x}},
  \linketaM{\phantom{x}}{X}{\lambda x.Y_{x}},
  \linketaM{\phantom{x}}{Z}{\lambda x.f \appsep G_{x}~x},
  \linketaM{x}{G_{x}}{\lambda y.H_{x~y}}}}

>>>>

\newcommand{\lhs}{\ensuremath{\mathrm{lhs}}\xspace}
\newcommand{\rhs}{\ensuremath{\mathrm{rhs}}\xspace}
\def\phantx{\phantom{x}}

\newcommand{\printMinipage}[2]{
  \listlength{#2}
  \foreach \x [count=\i] in #2
    {
      \begin{minipage}{3cm}
        $#1_\i : \x$ %
      \end{minipage}
      \ifthenelse{\equal{\i}{\thellength}}{}{
        \ifthenelse{\isodd{\i}}{|}{\\}
      }
    }
}

\newcommand{\printEntry}[1]{
  \listlength{#1}%
  \ifthenelse{\equal{0}{\thellength}}{}{
    \item[Entry pb:] 
    \foreach \x [count=\i] in #1
      {%
        \begin{minipage}{8cm}%
          $\mathcal{P}_\i : \x$ %
        \end{minipage}%
        \ifthenelse{\equal{\i}{\thellength}}{}{\\}%
      }%
  }%
}
\newcommand{\printItemComp}[3]{
  \listlength{#3}%
  \ifthenelse{\equal{0}{\thellength}}{}{
    \item[#1] \printMinipage{#2}{#3}
  }%
}

\newcommand{\printAll}[4]{
  \noindent%
  \begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Mapping:}]
    \printEntry{#1}%
    \printItemComp{Compil:}{\mathcal{T}}{#2}%
    \printItemComp{Mapping:}{m}{#3}%
    \printItemComp{Links:}{l}{#4}
  \end{description}
}

@@

In \cref{sec:basic-comp-limitations}, we have given two unification problems to
be run one after the other. In the following table we present the entry problem,
its compiled version, with the corresponding list of mapping and links.
%
\printAll
  {{\elpiIn{flam x\flam y\fapp[fuva F,y,x] = flam x\flam y\x},
    \elpiIn{flam x\fapp[fcon"f", fapp[fuva F, x], x] = fapp[fcon"f", flam x\x]}}}
  {{X = \lambda x.\lambda y.x, Z = f\appsep(\lambda x.x)}}
  {{\mapping{F}{G}{1}, \mapping{F}{H}{2}}}
  {{\linketaM{x}{Y_{x}}{\lambda y.H_{y~x}},
    \linketaM{\phantx}{X}{\lambda x.Y_{x}},
    \linketaM{\phantx}{Z}{\lambda x.f \appsep G_{x}~x}}}

@@

The complete problem to run for resolution is now:
%
\printAll
  {{}}
  {{X = \lambda x.\lambda y.x, 
    Z = f\appsep(\lambda x.x)}}
  {{\mapping{F}{H}{2}}}
  {{\linketaM{x}{Y_{x}}{\lambda y.H_{y x}},
    \linketaM{\phantom{x}}{X}{\lambda x.Y_{x}},
    \linketaM{\phantom{x}}{Z}{\lambda x.f \appsep G_{x}~x},
    \linketaM{x}{G_{x}}{\lambda y.H_{x~y}}}}
